PropOcData2

### 2020-04-06 R Analysis Scripts/PropOc Data 3D.Rmd
getting full data distributions

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)

@@

```
#Statistical exploration of the data.
Three individual runs were performed independently on each of the experiments. The output of each of them is the mean proportional occupancy and it's SD. So, if the runs follow a normal distribution, their variance should be similar.

```{r Plot PropOc mean and SD}
PlotPropOcMeanSD <- function(df, name) {
  plot1<- ggplot()+
    geom_linerange(data=df%>% filter(RunRep==1), aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Relation),size=1)+
    facet_wrap(Time~Relation, ncol = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(name, " proportional occupancy mean +/- SD"))+
    theme_minimal_grid()+
    background_grid()
  ggsave(paste0(name,".png"),plot = plot1, width = 17, height = 10)
  }

@@

PlotPropOcAllMeanSD <- function(relation) {
  plot1<- ggplot()+
    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
                   position = position_dodge(width =.8), size=.7)+
    facet_wrap(~Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
}
PlotPropOcAllMeanSD("Pa->Pa")
PlotPropOcAllMeanSD("Pa->Sa")
PlotPropOcAllMeanSD("Sa->Sa")
PlotPropOcAllMeanSD("Sa->Pa")
```
Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
```{r Plot CV}
PlotCVrelation <- function(relation){
  plot1<-ggplot()+
    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
               position = position_dodge(width =.8), size=4)+
    geom_hline(yintercept = 1, linetype = "dashed")+
    facet_wrap( ~ Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
  }
PlotCVrelation("Pa->Pa")
PlotCVrelation("Pa->Sa")
PlotCVrelation("Sa->Sa")
PlotCVrelation("Sa->Pa")
```

>>>>

```{r setup, include=FALSE}
library(pixmap)
library(rtiff)
library(reshape2)
library(gplots)
library(gdata)
library(plyr)
library(dplyr)
library(ggplot2)
library(cowplot)
library(tidyr)
library(purrr)
library(plotrix)
library(ggsignif)
library(rdist)
library("vcd")#this is fro fitting models to data
library(viridis)#color palette
library(gganimate)#gifs for ggplot

@@

```
#Statistical exploration of the data.
Three individual runs were performed independently on each of the experiments. The output of each of them is the mean proportional occupancy and it's SD. So, if the runs follow a normal distribution, their variance should be similar.
```{r Plot PropOc mean and SD}
PlotPropOcMeanSD <- function(df, name) {
  plot1<- ggplot()+
    geom_linerange(data=df%>% filter(RunRep==1), aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Relation),size=1)+
    facet_wrap(Time~Relation, ncol = 4)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(name, " proportional occupancy mean +/- SD"))+
    theme_minimal_grid()+
    background_grid()
  ggsave(paste0(name,".png"),plot = plot1, width = 17, height = 10)
  }

@@

PlotPropOcAllMeanSD <- function(relation) {
  plot1<- ggplot()+
    geom_linerange(data=combinedData %>% filter(Relation ==relation), 
                   aes(x=Distance,ymax=MeanPropOcc+SDPropOcc,ymin=MeanPropOcc-SDPropOcc, color = Strain, linetype =factor(BioRep), group = Experiment),
                   position = position_dodge(width =.8), size=.7)+
    facet_wrap(~Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy mean +/- SD"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,".png"),plot = plot1, width = 20, height = 10)
}
PlotPropOcAllMeanSD("Pa->Pa")
PlotPropOcAllMeanSD("Pa->Sa")
PlotPropOcAllMeanSD("Sa->Sa")
PlotPropOcAllMeanSD("Sa->Pa")
```
Another metric used is the coefficient of variation, CV, which is the ratio of the standard deviation to the mean.So, let's also visualize that.
```{r Plot CV}
PlotCVrelation <- function(relation){
  plot1<-ggplot()+
    geom_point(data=combinedData %>% filter(Relation =="Pa->Pa"), 
               aes(x=Distance,y = CV, color = Strain, shape = factor(BioRep), group = Experiment),
               position = position_dodge(width =.8), size=4)+
    geom_hline(yintercept = 1, linetype = "dashed")+
    facet_wrap( ~ Time, ncol = 3)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste0(relation, " proportional occupancy Coefficient of variation (SD/mean)"), linetype = "Biological Replicate")+
    theme_minimal_grid()+
    background_grid()+
    theme(plot.title = element_text(hjust = 0.5))
  ggsave(paste0(relation,"-CV.eps"),plot = plot1, width = 20, height = 10)
  ggsave(paste0(relation,"-CV.png"),plot = plot1, width = 20, height = 10)
  }
PlotCVrelation("Pa->Pa")
PlotCVrelation("Pa->Sa")
PlotCVrelation("Sa->Sa")
PlotCVrelation("Sa->Pa")
```
# Importing whole data sets to identify distribution of data
```{r whole data sets}
wt1.1Whole<-read.csv(paste0("/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/PropOcDataAll/wt1-1000-1.csv"),header = T)

GetHistPropOc <- function(df,timePoint, sources) {
  data<-df %>%  filter(TimePoint==timePoint) %>% filter(source==sources) %>% group_by(Distance) %>% filter(PropOc <1.02)
  dataList<-group_split(data)
  histogramList<-map(dataList, HistogramDistance)
  output<-bind_rows(histogramList)
  return(output)
}
HistogramDistance <- function(df) {
  #histogram<- hist(df$PropOc, breaks = seq.int(0,1.02,.01))
  histogram<- hist(df$PropOc)
  output<-data.frame(histogram$mids,histogram$counts)
  colnames(output)<-c("Value", "Frequency")
  output<-output %>% mutate(Distance = df$Distance[[1]]) %>% filter(!Frequency==0)
  return(output)
}
PlotAllPropOcData <- function(df, relation, timepoint) {
  ggplot()+
    geom_point(data = df,aes(x=Value,y=Frequency, color = Distance),size=2)+
    scale_y_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    #scale_x_log10( breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)))+
    labs(title =paste( relation, timepoint))+
    #scale_color_viridis(option = "D")+
    scale_color_gradientn(colours = rainbow(5))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5))
}

test<-wt1.1Whole %>% filter(source=="finalGG") %>% filter(TimePoint==5)
wt1.RR<-wt1.1Whole %>% filter(source=="finalRR")
hist(wt1.RR$PropOc)
hist(wt1.RR$PropOc, breaks = seq.int(0,1.01,.01))

wt1.GG<-GetHistPropOc(wt1.1Whole, 0, "finalGG")
wt1.RG<-GetHistPropOc(wt1.1Whole, 0, "finalRG")
wt1.RR<-GetHistPropOc(wt1.1Whole, 0, "finalRR")
wt1.GR<-GetHistPropOc(wt1.1Whole, 0, "finalGR")

wt1.GG.5<-GetHistPropOc(wt1.1Whole, 5, "finalGG")
wt1.RG.5<-GetHistPropOc(wt1.1Whole, 5, "finalRG")
wt1.RR.5<-GetHistPropOc(wt1.1Whole, 5, "finalRR")
wt1.GR.5<-GetHistPropOc(wt1.1Whole, 5, "finalGR")

PlotAllPropOcData(wt1.GG)
PlotAllPropOcData(wt1.GR)
PlotAllPropOcData(wt1.RR)
PlotAllPropOcData(wt1.RG)

PlotAllPropOcData(wt1.GG.5,5, "finalGG")
PlotAllPropOcData(wt1.GR.5,5, "finalGR")
PlotAllPropOcData(wt1.RR.5,5, "finalRG")
PlotAllPropOcData(wt1.RG.5,5, "finalRG")
